---
title: "Data analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Prediction - Estimating the value/conditional distribution P(Y|X) of one variable given the values of others.

Supervised learning - Solving a prediction problem when the data includes both X and Y, for example linear or logistic regression.

Unsupervised learning - Solving a prediction problem when the data only includes X, for example clustering.

Density estimation/generative modeling - Estimating the distribution P(Y) of some variables.

```{r}
n = 100
X = rnorm(n)
Y = X + rnorm(n)/10
head(cbind(X, Y))
```
```{r}
plot(X, Y, main = "Linear regression - continuous predictor")
abline(lm(Y ~ X), col = 2)
```
```{r}
Y = rbinom(n, 1, 1/(1 + exp(-X)))
head(cbind(X, Y))
```
```{r}
plot(X, Y, main = "Logistic regression - continuous predictor")
points(X, fitted(glm(Y ~ X, binomial)), col = 2)
```
```{r}
X = rbinom(n, 1, 0.5)
Y = X + rnorm(n)/10
head(cbind(X, Y))
```
```{r}
rb = boxplot(Y ~ X, main = "Linear regression - discrete predictor")
points(1:2, predict(lm(Y ~ X), newdata = data.frame(X = 0:1)), col = 2)
```

```{r}
Y = rbinom(n, 1, ifelse(X, 1/4, 3/4))
head(cbind(X, Y))
```
```{r}
plot(table(X, Y), main = "Logistic regression - discrete predictor")
plot(table(X, (fitted(glm(Y ~ X, binomial)) > 0.5) * 1), col = 2, main = "Logistic regression - discrete predictor")
```



